Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-10-22 saner/paper.tex
Background & related work

The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method. Applying this technique entails moving functionality in the body of a method to a new method. To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.

@@

\section{Related Work}\label{sec:relatedwork}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@

\todo{Add more related work?}

>>>>

\subsection{Clone Types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout, and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.
A higher type of clone means that it is harder to detect and refactor. Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

\subsection{Refactoring}
The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method. Applying this technique entails moving functionality from the body of a method to a new method. To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.

@@

\section{Related Work}\label{sec:relatedwork}
\subsection{Clone Context analysis}
A study by Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods. The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations. The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.

Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}. They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types. We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.

\subsection{JDeodorant}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@
